Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-28 main-disk-model.tex
new text in chapter "Model"

The goal is to execute the workflow on a heterogeneous system, denoted as $\cluster$, which
consists of $k$ processors $p_1, \dots, p_k$.
Each processor $p_j$ ($1 \leq j \leq k$) has an individual memory of size $M_j$ and a speed~$s_j$.
All processors have access to a common disk space of unlimited size.
All communications happen over the disk - after one processor has finished writing data there, another one can read
it into its individual memory.
We can decide to evict some data from the individual memory onto the disk to free space in the individuaö memory.
    This data can be read back into memory at any time later.

The execution time of a single task~$u\in V$ on a processor~$p_j$ is expressed as $\frac{w_u}{s_j}$.
We assume that all processors are connected with the same bandwidth~$\beta$.
%    \hmey{Maybe mention that variable bandwidths are part of future work...?}

We keep track of the current ready time of each processor and each communication
channel, $\rt_j$ and $\rt_{j,j'}$, for each processor $j$ and all pairs~$(j,j')$.
Initially, all the ready times are set to~$0$.
We also keep track of the currently available memory, $availM_j$ and $availC_j$,
on the processor memory and communication buffer, respectively.
Furthermore, $\PD_j$ is a priority queue with the {\em pending data}
that are in the memory of size $\MM_j$ but may be evicted to be communicated if
more memory is needed on~$p_j$. They are ordered by non-decreasing size and
correspond to some $c_{u,v}$.

@@

@@

The goal is to find a schedule of the DAG~$G$ for the $k$ processors,
so that the makespan (total execution time) is minimized while
respecting memory constraints. If a processor runs out of memory to execute
a task mapped on it, the schedule is said to be {\em invalid}.

>>>>

The goal is to execute the workflow on a heterogeneous system, denoted as $\cluster$, which
consists of $k$ processors $p_1, \dots, p_k$.
Each processor $p_j$ ($1 \leq j \leq k$) has an individual memory of size $M_j$ and a speed~$s_j$.
All processors have access to a common disk space of unlimited size, but of much slower speed.
All communications happen over the disk - after one processor has finished writing data there, another one can read
it into its individual memory.
We can decide to evict some data from the individual memory onto the disk to free space in the individual memory.
This data can later be read back into memory at any time, or transferred to another processor.

If the entire memory required by the task ~$u\in V$ fits in the free memory of a processor~$p_j$,
    then the execution time of this task on this processor is expressed as $\frac{w_u}{s_j}$.
If the memory requirement of the task exceeds the available memory on the processor, the task can still be executed there,
    albeit slower.
The part of memory requirement that exceeds the available memory will be offloaded to the disk, slowing down the execution.

    \[
        w_{real} = \frac{w_u}{s_j} * (1 + (m_i - M_j)/m_i ) * q_s.

    \]
where $q_s$ sit he slowdown coefficient.
%We assume that all processors are connected with the same bandwidth~$\beta$.
%    \hmey{Maybe mention that variable bandwidths are part of future work...?}

Multiple processors can communicate with the disk in parallel, but the communication of each processor  with the disk is sequential.
The processor can read and write at the same time, but only one file can be read and only one written at any point in time.
We keep track of the current ready times of each processor $j$ , ready time for computation $\rt_j^c$,
ready time for writing $\rt_j^w$, and ready time for reading $\rt_j^r$.
Initially, all the ready times are set to~$0$.
We also keep track of the currently available memory, $availM_j$ on the processor memory.

Furthermore, $\PD_j$ is a priority queue with the {\em pending data}
that are in the memory of size $\MM_j$ but may be evicted to the disk
more memory is needed on~$p_j$.
They are ordered by non-decreasing size and correspond to some $c_{u,v}$.
When scheduling a tass, the decision has to be made to execute this task on a processor with enough memory
    without slowdown, but with possibly more time to read the input files, or to execute the same task
    on a processor with less memory (and hence a slowdown), but potentially with a higher processor speed or with less times
    spent reading files.

@@

\subsection{Scheduling approach - general description}

In the first step, we order the tasks by non-increasing ranks (e.g. their bottom levels).
In the next step, we repeatedly schedule ready tasks.
For each task, we first choose the best processor to put it on - the one that minimizes the expected finishing time.
For each processor, we compute this earliest finishing time by first calculating the earliest starting time on this processor.
    It is computed as the maximum of the ready time of computation on this processor, and the time to read input files.

@@

The goal is to find a schedule of the DAG~$G$ for the $k$ processors,
so that the makespan (total execution time) is minimized while
respecting memory constraints. \skug{do we still formulate it like that?}
    %If a processor runs out of memory to execute
%a task mapped on it, the schedule is said to be {\em invalid}.
